---
title: "ASS_5 - Metaanalysis of pitch in schizophrenia"  
author: "Amalie Lysgaard Andersen"
date: "30/11/2018"
output: word_document
---

```{r setup, include=FALSE}
setwd("~/Library/Mobile Documents/com~apple~CloudDocs/4. Aarhus Universitet/3. Semester/1. Experimental Methods lll/R FOLDER/Meta-analysis/Meta-analysis") 
 
library(pacman)
p_load(metafor, ggplot2, tidyverse, dplyr, lme4, forestplot,plyr)

detach(package:plyr)
library(dplyr)
```

# Building on the shoulders of giants: meta-analysis
 
## Questions to be answered

1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia? Report how many papers report quantitative estimates, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 

```{r Cleaning data}
# Loading data 
data <- read.csv("Assignment5_MetaAnalysis_SR_SCHIZO.csv")   

# Removing studies (note: the model filters them out anyway)
data_clean <- data[!with(data,is.na(PITCH_F0_SZ_SD) & is.na(PITCH_F0SD_SZ_SD)),]
# We exclude all studies in which only sample size is reported (24 studies are left)

#Reading descriptions 
#data_clean$ACOUST_ANA_DESCR
```

```{r Models}
### PITCH MODEL 
pitch = escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0_SZ_M, m2i=PITCH_F0_HC_M, sd1i=PITCH_F0_SZ_SD, sd2i=PITCH_F0_HC_SD, data = data_clean) 

# Mixed effects model 
model_mean <- lmer(yi ~ 1 + (1 | StudyID), weights = 1/vi, data=pitch, control= lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_mean)

# Meta-analysis optimisation
model_mean_meta <- rma(yi, vi, data = pitch, slab=StudyID)
forest(model_mean_meta) 



### PITCH VARIABILITY MODEL
pitch_var = escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0SD_SZ_M, m2i=PITCH_F0SD_HC_M, sd1i=PITCH_F0SD_SZ_SD, sd2i=PITCH_F0SD_HC_SD, data = data_clean)

# Mixed effects model 
model_var <- lmer(yi ~ 1 + (1 | StudyID), weights = 1/vi, data=pitch_var, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_var)

# Meta-analysis optimisation
model_var_meta <- rma(yi, vi, data = pitch_var, slab=StudyID) 
forest(model_var_meta) 

# Calling values
model_mean_meta
model_var_meta

confint(model_mean_meta, levels = .95)
confint(model_var_meta, levels = .95)

summary(model_mean_meta)
summary(model_var_meta)
```

```{r Testing influential studies}
# Pitch mean 
inf <- influence(model_mean_meta)
print(inf)
plot(inf)
 
# pitch variance
inf2 <- influence(model_var_meta)
print(inf2)
plot(inf2)
```

```{r Funnel plot}
# Pitch 
funnel(model_mean_meta, main = "Random-Effects Model", xlab = "Standardized Mean Difference")

#Range 
funnel(model_var_meta, main = "Random-Effects Model", xlab = "Standardized Mean Difference")


confint(model_var_meta, level =.95)
```

```{r Add. data }
# Funnel plot asymmetry - Pitch mean 
regtest(model_mean_meta) 
ranktest(model_mean_meta)

# Funnel plot asymmetry - Pitch variability 
regtest(model_var_meta)
ranktest(model_var_meta) 

model_var_meta
```


2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots
```{r Models}
# Load data from ASS3 
data_ass3 <- read.csv("ASS3_data.csv")

diagnosis <- c("Control", "Control", "Control", "Schizophrenia", "Schizophrenia", "Schizophrenia") 
study <- c(1, 2, 3, 1, 2, 3)
diag_stud <- as.data.frame(diagnosis)
diag_stud$study <- study

# Predicting models
modelmodel_mean <- lmer(mean ~ diagnosis + (1|trial) + (1|study) + (1|ID), data_ass3, REML = F)
modelmodel_var <- lmer(sd ~ diagnosis + (1|study) + (1|trial) +(1|ID), data_ass3, REML = F)

#Get optimal "mean" by predicting data for a matrix for 3 studies
predict(modelmodel_mean, re.form = ~ (1| study),  newdata = diag_stud, allow.new.levels = T)
predict(modelmodel_var, re.form = ~ (1| study),  newdata = diag_stud, allow.new.levels = T)

# Dataframes
sd_mean <- data_ass3 %>% 
   dplyr::group_by(diagnosis, study) %>%
   dplyr::summarise(sd = sd(mean))

sd_sd <- data_ass3 %>% 
   dplyr::group_by(diagnosis, study) %>%
   dplyr::summarise(sd = sd(sd))


# Filtering # of participants in different variables
data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Control" & study == 1) %>%
  summarise() %>%
  nrow()
#[1] 36

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Schizophrenia" & study == 1) %>%
  summarise %>%
  nrow()
#[1] 34

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Control" & study == 2) %>%
  summarise %>% 
  nrow()
#[1] 23

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Schizophrenia" & study == 2) %>%
  summarise %>%
  nrow()
#[1] 23

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Control" & study == 4) %>%
  summarise() %>%
  nrow()
#[1] 16

data_ass3 %>% 
  group_by(ID) %>%
  filter(diagnosis == "Schizophrenia" & study == 4) %>%
  summarise() %>%
  nrow()
#[1] 19

#Adding values to a dataframe with similar columns
listoflists <- list(StudyID = c(49, 50, 51), 
                    ArticleID = 47, 
                    SAMPLE_SIZE_HC = c(36, 23, 16), 
                    SAMPLE_SIZE_SZ = c(34, 23, 19),
                   

                    PITCH_F0_HC_M = c(142.4939, 123.8641, 137.0162),
                    PITCH_F0_SZ_M = c(156.2813, 137.6516, 150.8036), 
                    
                    PITCH_F0_HC_SD = c(51.03645, 34.76154, 46.62267),
                    PITCH_F0_SZ_SD = c(54.74809, 60.50305, 46.65587),
                    
                    PITCH_F0SD_HC_M = c(24.72409, 27.32127, 25.47117),
                    PITCH_F0SD_SZ_M = c(22.07029, 24.66747, 22.81737),
                    
                    PITCH_F0SD_HC_SD = c(15.79852, 20.48901, 21.31672),
                    PITCH_F0SD_SZ_SD = c(29.54196, 47.36456, 12.57604))

ass3 <- as.data.frame(listoflists)

ass3$ACOUST_ANA_DESCR = NA
ass3$DESCRIPTION = NA
ass3$COMMENTS = "At least we tried xD"
ass3$frequency = NA
ass3$Title = "Diagnosis On Basis of Pitch"
ass3$Authors = "Tinka et al" 
ass3$Article = NA
ass3$Year_publication = "2018"
ass3$pitch_f0_variability = NA 

ass3$Authors <-  c("Tinka et al", "Pyrus et al", "Rudolph et al") 

# as.factor(ass3$ACOUST_ANA_DESCR)
# as.factor(ass3$DESCRIPTION)
# as.factor(ass3$COMMENTS)
# as.factor(ass3$frequency)
# as.factor(ass3$Title)
# as.factor(ass3$Authors)
# as.factor(ass3$Article)

data_all <- rbind(data_clean, ass3)
``` 

```{r Cohen's D Models}
# Cohens D for mean 
pitch_mean_all = escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0_SZ_M, m2i=PITCH_F0_HC_M, sd1i=PITCH_F0_SZ_SD, sd2i=PITCH_F0_HC_SD, data = data_all)
 
pitch_var_all = escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0SD_SZ_M, m2i=PITCH_F0SD_HC_M, sd1i=PITCH_F0SD_SZ_SD, sd2i=PITCH_F0SD_HC_SD, data = data_all)


# Mixed effects model 
model_mean_all <- lmer(yi ~ 1 + (1 | StudyID), weights = 1/vi, data= pitch_mean_all, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_mean_all)

model_var_all <- lmer(yi ~ 1 + (1 | StudyID), weights = 1/vi, data= pitch_var_all, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_var_all)


# Meta-analysis optimisation
model_mean_2 <- rma(yi, vi, data = pitch_mean_all, slab=StudyID)
model_mean_2
forest(model_mean_2)

model_var_2 <- rma(yi, vi, data = pitch_var_all, slab=StudyID)
model_var_2
forest(model_var_2)


# Calling values
model_mean_2
model_var_2
model_mean_meta

confint(model_mean_2, level = .95) 
confint(model_var_2, level = .95)
confint(model_mean_meta, level = .95) 

summary(model_mean_2)
summary(model_var_2)
summary(model_mean_meta)
```

```{r Funnel}
# Pitch 
funnel(model_mean_2, main = "Random-Effects Model", xlab = "Standardized Mean Difference")

# Range
funnel(model_var_2, main = "Random-Effects Model", xlab = "Standardized Mean Difference")
```

```{r Excl study 15}
#Plots with exclusion of study 15 
test_var <- pitch_var_all[!pitch_var_all$StudyID == 15,] 

model_var_3 <- rma(yi, vi, data = test_var, slab=StudyID)
model_var_3

forest(model_var_3)
funnel_var_all_v3 = funnel(model_var_3, main = "Random-Effects Model", xlab = "Standardized Mean Difference")
``` 


3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.

## Tips on the process to follow:
- Download the data on all published articles analyzing pitch in schizophrenia (on gitlab)
- Look through the dataset to find out which columns to use, and if there is any additional information written as comments (real world data is always messy!).
    * Hint: Make sure you read the comments in the columns: `pitch_f0_variability`, `frequency`, `Title`,  `ACOUST_ANA_DESCR`, `DESCRIPTION`, and `COMMENTS`
- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
 . first try using lmer (to connect to what you know of mixed effects models)

- Build a forest plot of the results (forest(model))
- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?
- Now look at the output of rma() and check tau and I2
